Automated Software Engineering Final Paper (Working Title)

### 2015-12-12 paper/paper.tex
Added Nagappan paper to related work

>>>>

While there have been plenty of studies about predicting software faults based on the code itself, few studies have looked at organizational structure as a factor. Nagappan et al \cite{Nagappan} used organizational metrics, such as number of engineers, edit frequency, and organizational intersection factor to predict fault-proneness. The authors compared the effectiveness of the resulting model with alternative models which use traditional software metrics, like code churn and code complexity. They found that the model derived from organizational metrics had better precision and recall than others derived from software metrics, meaning they can also be effective indicators of failure-proneness.
